---
title: "AIRTOOL PROTOTYPE--not intended for public consumption"
format: 
  dashboard:
    theme: spacelab
    orientation: columns
    # embed-resources: true
    header-includes:
      - '<meta name="color-scheme" content="light">'

resources:
  - readme_md_files
server: shiny
---

```{=html}
<style>
  .plot-container, .shiny-text-output, .panel, .card {
    border: none;
    box-shadow: none;
  }
  .custom-text {
    font-size: 20px;
    color: green;
    font-weight: bold;
  }
</style>
```

```{=html}
<style> .main-container { max-width: unset; } </style>
<div id="style-test" style="background-color: white; color: black; position: absolute; left: -9999px;"></div>
```

```{javascript}
const testElem = document.getElementById("style-test");
const computedBg = window.getComputedStyle(testElem).backgroundColor;
const computedColor = window.getComputedStyle(testElem).color;

if (computedBg !== "rgb(255, 255, 255)" || computedColor !== "rgb(0, 0, 0)") {
  alert("It appears a dark mode extension might be overriding the styles. Please disable it for the best experience.");
}

```

```{r}
#| context: setup
#| echo: false
#| include: false

# suppressMessages(library(tidyverse))
suppressMessages(library(AIPW))
suppressMessages(library(DiagrammeR))
suppressMessages(library(dplyr))
suppressMessages(library(e1071))
suppressMessages(library(ggplot2))
suppressMessages(library(hal9001))
suppressMessages(library(here))
suppressMessages(library(nnet))
suppressMessages(library(randomForest))
suppressMessages(library(readr))
suppressMessages(library(rJava))
suppressMessages(library(rpart))
suppressMessages(library(scales))
suppressMessages(library(shiny))
suppressMessages(library(shinyWidgets))
suppressMessages(library(sl3))
suppressMessages(library(tidyr))
suppressMessages(library(tmle3))
suppressMessages(library(xgboost))
suppressMessages(library(jsonlite))
suppressMessages(library(foreach))
suppressMessages(library(doParallel))
suppressMessages(library(earth))
suppressMessages(library(hash))
suppressMessages(library(sets))


AIRHome <- here()
setwd(AIRHome)
set.seed(123)


# Nick, I significantly reduced the complexity of tetrad_utils. Most of what it
# was doing is no longer needed.

source("scripts/AIR_functions.R")

disconnectMessage2()
actionButton("disconnect", "Disconnect the app")

if (!dir.exists(paste0(AIRHome, "/data/"))) {
  dir.create(paste0(AIRHome, "/data/"), recursive = TRUE)
}

if (!dir.exists(paste0(AIRHome, "/input/"))) {
  dir.create(paste0(AIRHome, "/input/"), recursive = TRUE)
}

if (!dir.exists(paste0(AIRHome, "/plots/"))) {
  dir.create(paste0(AIRHome, "/plots/"), recursive = TRUE)
}

if (!dir.exists(paste0(AIRHome, "/logs/"))) {
  dir.create(paste0(AIRHome, "/logs/"), recursive = TRUE)
}

if (Sys.info()["sysname"] == "Linux") {
  source("scripts/tetrad_utils.R")
  source("scripts/TetradSearch.R")
  
  if (!dir.exists(paste0(AIRHome, "/data/"))) {
    dir.create(paste0(AIRHome, "/data/"), recursive = TRUE)
  }
  
  if (!dir.exists(paste0(AIRHome, "/input/"))) {
    dir.create(paste0(AIRHome, "/input/"), recursive = TRUE)
  }
  
  if (!dir.exists(paste0(AIRHome, "/plots/"))) {
    dir.create(paste0(AIRHome, "/plots/"), recursive = TRUE)
  }
  
  if (!dir.exists(paste0(AIRHome, "/logs/"))) {
    dir.create(paste0(AIRHome, "/logs/"), recursive = TRUE)
  }
  # Setup Java and Tetrad
  ## if running on local machine, uncomment out the next line
  # setup_tetrad_environment()
  
  .jinit()
  # .jinit(parameters = "-verbose:class")
  .jaddClassPath(TETRAD_PATH)
  
  java_version <- .jcall("java/lang/System", "S", "getProperty", "java.version")
  # print(paste("Java version:", java_version))
} 

## create a log file, then remove any logs over 30 days old
log_file <- paste0("logs/", format(Sys.time(), "%Y-%m-%d_%H-%M-%S"), "_error_log.txt")
cat("Begin Log\n", file = log_file, append = FALSE)
# Define the log directory and calculate the time threshold (7 days ago)
log_dir <- "logs"
time_threshold <- Sys.time() - 30 * 24 * 60 * 60  # 30 days in seconds

# List all log files in the directory
log_files <- list.files(log_dir, full.names = TRUE)

# Get file information for each file
files_info <- file.info(log_files)

# Identify files where the modification time is older than the threshold
old_files <- rownames(files_info)[files_info$mtime < time_threshold]

# Remove the old log files
if (length(old_files) > 0) {
  file.remove(old_files)
}
```

# Docs

```{r include-info, echo=FALSE, results='asis'}
# Read the file and output its content as-is
# cat(paste(readLines("info.qmd"), collapse = "\n"))
knitr::opts_knit$set(root.dir = AIRHome)
cat(knitr::knit_child("info.qmd", quiet = TRUE))
```

# Analysis of Bias

##  {.sidebar}

```{r}
h4("Step 1: Upload your data")
fileInput("file1", "", accept = ".csv")
br()
uiOutput('step2')
uiOutput('ui_file2')
br()
uiOutput('ui_buildButton')
br()
uiOutput('step3')
uiOutput('xvar')
uiOutput('ui_threshold_x')
br()
uiOutput('yvar')
uiOutput('ui_threshold_y')
br()
uiOutput('ui_updateButton')
uiOutput('step4')
uiOutput('ui_model_exist')
uiOutput('ui_model_upload')
uiOutput('ui_ate_upload')
uiOutput('ui_goButton')
uiOutput('ui_dl_btn')

```

## Column {width = "40%"}

```{r}
# grVizOutput('blankGraph')
uiOutput('ui_graph_pane')
```

## Column {width = "60%"}

```{r}
# plotOutput('histogram_x', height = "50%")
uiOutput('second_column_content')
# uiOutput('ui_top_right_pane')
```

<!-- #### Row -->

<!-- ```{r} -->
<!-- # plotOutput('histogram_y', height = "50%") -->
<!-- # uiOutput('ui_bottom_right_pane') -->
<!-- ``` -->

<!-- # Results -->

<!-- ## Column {width="60%"} -->

<!-- ```{r} -->
<!-- #| padding: 0px -->
<!-- ##| title: "Causal Discovery" -->
<!-- uiOutput('ui_graphViz') -->
<!-- ``` -->

<!-- ## Column {width="40%"} -->

<!-- ```{r} -->
<!-- #| padding: 0px -->
<!-- # UI Output for ribbon plot -->
<!-- uiOutput("second_column_content") -->

<!-- ``` -->

```{r}
#| context: server


### variable declarations --------------------------------------------------------------
calc_complete <- reactiveVal(FALSE)
graph_complete <- reactiveVal(FALSE)
graph_update <- reactiveVal(FALSE)
file_check <- reactiveVal(FALSE)


# sendSweetAlert(
#   session = shiny::getDefaultReactiveDomain(),
#   title = "Welcome to the AIR Tool!",
#   text = "For best results, please view the tool without forced darkmode readers.",
#   type = "info",
#   btn_labels = "Continue",
#   btn_colors = "#3085d6",
#   closeOnClickOutside = TRUE,
#   showCloseButton = FALSE
#   )

### input reactives -------------------------------------------------------------------
model_in <- reactive({
  req(input$model_in)
  #loading the model
  model_in = read_rds(input$model_in$datapath)
  cat(paste0(Sys.time(), " - ","Read in model: " ,input$model_in$datapath, "\n"), file = log_file, append = TRUE)

  # model_in = read_rds("input/model.rda")
  # ext <- tools::file_ext(input$modelFile$datapath)
    
  #model_in <- switch(ext,
  #         "rds" = read_rds(input$modelFile$datapath),  # R models
  #         "model" = xgb.load(input$modelFile$datapath),  # XGBoost model
  #         stop("Unsupported file type")
  #  )
  
  return(model_in)
})

df <- reactive({
  df <- read_csv(input$file1$datapath, col_types = cols(.default = col_number()))
  cat(paste0(Sys.time(), " - ","Read in data file: ", input$file1$datapath, "\n"), file = log_file, append = TRUE)
  # df <- read_csv("input/data.csv", col_types = cols(.default = col_number()))
  continuous_columns <- c(1, ncol(df))
  df[, continuous_columns] <- apply(df[, continuous_columns], 2, as.numeric)
  return(df)
})

# knowledge <- read_csv("input/knowledge.csv", col_names = T)
knowledge <- reactive({
  req(input$file2)  # Make sure the file is uploaded
  path2 <- input$file2$datapath
  cat(paste0(Sys.time(), " - ","Read in knowledge file: " ,input$file2$datapath, "\n"), file = log_file, append = TRUE)

  extension <- tolower(tools::file_ext(path2))
  
  if (extension == "csv") {
    knowledge_in <- read_csv(path2, col_names = TRUE)
  } else if (extension == "xlsx") {
    knowledge_in <- readxl::read_excel(path2, col_names = TRUE)
  } else {
    sendSweetAlert(
      session = shiny::getDefaultReactiveDomain(),
      title = "Upload Failed",
      text = "Unsupported file extension. Please upload a CSV or XLSX file.",
      type = "warning",
      btn_labels = "Continue",
      btn_colors = "#3085d6",
      closeOnClickOutside = TRUE,
      showCloseButton = FALSE
    )
    return(NA)
  }
  
  # Process the data with fix_knowledge
  fixed <- fix_knowledge(knowledge_in)
  # Check the outcome of fix_knowledge
  if (is.character(fixed)) {
    sendSweetAlert(
      session = shiny::getDefaultReactiveDomain(),
      title = "Upload Failed",
      text = fixed,
      type = "warning",
      btn_labels = "Continue",
      btn_colors = "#3085d6",
      closeOnClickOutside = TRUE,
      showCloseButton = FALSE
    )
    return(NA)
  } else {
    file_check(TRUE)  # Set the reactiveVal if all is good
    return(fixed)
  }
})



### event observations ----------------------------------------------------------------
options(shiny.error = function() {
  tb <- traceback()  # Capture the call stack
  showModal(modalDialog(
    title = "An error occurred",
    paste0("AIR Tool crashed. See log file, ", log_file, ", for details"),
    easyClose = TRUE
  ))
})

observeEvent(input$disconnect, {
    session$close()
  })

observeEvent(input$file2, {
  # Call the reactive to force its evaluation
  result <- knowledge()
  # Optionally, you can print or log the result for debugging
  #print(result)
})

observeEvent(input$updateButton, {
  ### AIR Step 2 ---------------
  # assign global variables
  assign("df_vars",
         data.frame("var" = c("TV","OV"),
                    "val" = c(input$xvar, input$yvar)),
         envir = .GlobalEnv)
  # assign("df_vars", data.frame("var" = c("TV","OV"), "val" = c(xvar, yvar)), envir = .GlobalEnv)
  # source_python(paste0(AIRHome, "/scripts/identify.py"))
  if (Sys.info()["sysname"] == "Linux") {
    param1 = df_vars$val[1]
    param2 = df_vars$val[2]
    param3 = paste0(AIRHome, "/graphtxt.txt")

    rust_bin = "identify"
    # system2() returns the output as a character vector (one element per line).
    json_output <- system2(rust_bin,
                           args = c(paste0("--param1=", param1),
                                    paste0("--param2=", param2),
				    paste0("--param3=", param3)),
                           stdout = TRUE)
    
    # json_output is a character vector. If the Rust program only prints a single line
    # of JSON, json_output[1] will hold the entire JSON string.
    parsed <- fromJSON(json_output[1])
    
    # Now `parsed` should be a list with two elements: $vector1 and $vector2
    Z1 <- parsed$vector1
    Z2 <- parsed$vector2
  } else {
    source("scripts/identify.R")
  }
  Z1 = strsplit(gsub("(\\}|\\{|\\')","",toString(Z1), perl = T), ", ")[[1]]
  Z2 = strsplit(gsub("(\\}|\\{|\\')","",toString(Z2), perl = T), ", ")[[1]]
  # Z1 = "region_sensitivity"
  # Z2 = "mission_urgency"
  ### overlaps in function with df_vars. consider combining and slimming down. consider appending to df_vars ---------
  Zvars_loc <- data.frame("name" = character(),
                          "grp" = character(),
                          "Z" = character())

  for (i in Z1) {
    Zvars_loc <- rbind(Zvars_loc, c(df_vars[df_vars$var == "TV",]$val, "Z1", i))
  }

  for (i in Z2) {
    Zvars_loc <- rbind(Zvars_loc, c(df_vars[df_vars$var == "TV",]$val, "Z2", i))
  }

  colnames(Zvars_loc) <- c("name", "grp", "Z")
  assign("Zvars", Zvars_loc, envir = .GlobalEnv)
  cat("Graph Updated\n", file = log_file, append = TRUE)

  if (graph_update()) {
    sendSweetAlert(
      session = shiny::getDefaultReactiveDomain(),
      title = "Causal Graph Updated",
      text = NULL,
      type = "success",
      btn_labels = "Continue",
      btn_colors = "#3085d6",
      closeOnClickOutside = TRUE,
      showCloseButton = FALSE,
      )
  }
  graph_update(TRUE)

  # update the graph
  output$blankGraph <- renderGrViz({
  req(graph_complete())
  dot <- readLines("dotfile.txt")  
  if (graph_update()) {
    dot <- change_node_color(dot, input$xvar, "'#FFC107'")
    dot <- change_node_color(dot, input$yvar, "'#FFC107'")
    dot <- change_node_color(dot, Zvars[Zvars$grp == "Z1",]$Z, "'#9394A2'")
    dot <- change_node_color(dot, Zvars[Zvars$grp == "Z2",]$Z, "'#D4C7C7'")
  }
  grViz(dot, )
  })

  cat(paste0(Sys.time(), " - ","Selected X variable: ", input$xvar,"\n"), file = log_file, append = TRUE)
  cat(paste0(Sys.time(), " - ","Selected Y variable: ", input$yvar,"\n"), file = log_file, append = TRUE)
  cat(paste0(Sys.time(), " - ","Selected X threshold: ", input$tv_dir," ", input$tv_threshold,"\n"), file = log_file, append = TRUE)
  cat(paste0(Sys.time(), " - ","Selected Y threshold: ", input$ov_dir," ", input$ov_threshold,"\n"), file = log_file, append = TRUE)

})

observeEvent(input$buildButton, {
  ### AIR Step 1 ----------------
    if (Sys.info()["sysname"] == "Linux") {
      graph <- AIR_getGraph(df(), knowledge()) # prod
      dot <- .jcall("edu/cmu/tetrad/graph/GraphSaveLoadUtils", "Ljava/lang/String;", "graphToDot", graph) # prod
    } else {
      graph <- read_file("graphtxt.txt") # test
      dot <- read_file("dotfile.txt") # test
    }
  
    # graph <- AIR_getGraph(df, knowledge)
    
    # graph_data <- .jcall(graph, "Ljava/lang/String;", "toString")
    # writeLines(graph_data, "graphtxt.txt")
  
    # Visualize the resulting graph
    # visualize_graph(graph)
    write(gsub("(?m)^\\s*\\n", "", dot, perl = TRUE), "dotfile.txt")
  
    output$blankGraph <- renderGrViz({
      req(graph_complete())
      cat("Graph Built\n", file = log_file, append = TRUE)
  
      dot <- readLines("dotfile.txt")  
      # for (node in names(df())) {
      #   dot <- change_node_color(dot, node, "'#ffffff'")
      # }
  
      grViz(dot)
    })
    
    if (graph_complete()) {
      sendSweetAlert(
        session = shiny::getDefaultReactiveDomain(),
        title = "Your Causal Graph is Ready",
        text = NULL,
        type = "success",
        btn_labels = "Continue",
        btn_colors = "#3085d6",
        closeOnClickOutside = TRUE,
        showCloseButton = FALSE,
        )
    }
    graph_complete(TRUE)
    
})
  
observeEvent(input$goButton, {
  cat(paste0(Sys.time(), " - ","Selected model_exist: ", input$model_exist,"\n"), file = log_file, append = TRUE)
  cat(paste0(Sys.time(), " - ","Selected ate_in: ", input$ate_in,"\n"), file = log_file, append = TRUE)

  withProgress(message = 'Building Causal Graph', style = "notification", value = 0.1, {

    incProgress(0.1, message = "Calculating Adjustment Sets", detail = "Creating Compute Environment")

    ### AIR Step 3 ----------------
    
    write_csv(df(), paste0(AIRHome, "/data/datafile.csv"), col_names = T)
    # write_csv(df, paste0(AIRHome, "/data/datafile.csv"), col_names = T)

    incProgress(0.1, message = "Estimating Causal Effects")
    assign("model_yn",
           input$model_exist,
           envir = .GlobalEnv)

    assign("model_ate",
           input$ate_in,
           envir = .GlobalEnv)

    # assign("model_yn", model_exist, envir = .GlobalEnv); assign("model_ate", ate_in, envir = .GlobalEnv)

    write.csv(file = "Results.csv",
              x = data.frame("Row" = vector(),
                             "Treatment" = vector(),
                             "Group" = vector(),
                             "Mean" = vector(),
                             "LCI" = vector(),
                             "UCI" = vector()),
              row.names = FALSE)
    
    if (Sys.info()["sysname"] == "Linux") {
      Sys.chmod("Results.csv", mode = "0777")
    }
    incProgress(0.1, message = "Calculating Adjustment Sets", detail = "Creating Compute Environment")
      cat("Calculating Adjustment Sets\n", file = log_file, append = TRUE)

    ### have to figure out how many cores there are
    ## for now, just hardcode that in
    
    tryCatch({
        # foreach(i = unique(Zvars$name)) %dopar% {
        #   foreach(j = unique(Zvars$grp)) %do% {
        combos <- expand.grid(i = unique(Zvars$name), j = unique(Zvars$grp), stringsAsFactors = F) 
        tv_dir_val <- input$tv_dir
        tv_threshold_val <- input$tv_threshold
        ov_dir_val <- input$ov_dir
        ov_threshold_val <- input$ov_threshold
        
        # How many cores does your CPU have
        n_cores <- detectCores()
        n_cores <- min(nrow(combos), n_cores - 1)
        
        # Register cluster
        cluster <- makeCluster(n_cores)
        clusterEvalQ(cluster, {
          library(tmle3)
          library(sl3)
        })
        registerDoParallel(cluster)
        
        }, error = function(e) {
          errMsg <- sprintf("Failed setting up parallel clusters", conditionMessage(e))
          cat(errMsg, file = log_file, sep = "\n", append = TRUE)
          NULL
        })

    tryCatch({
      incProgress(0.1, detail = paste0("\nCalculating ATE for multiple Adjustment Sets"))
      }, error = function(e) {
        NULL
    })
    
    foreach(k = 1:nrow(combos), 
            .packages = c("AIPW", "dplyr", "e1071", "earth", "ggplot2", "hal9001", "nnet", "randomForest", "readr", "scales", "sl3", "tidyr", "tmle3", "xgboost", "foreach", "doParallel", "shiny"),
            .export = c("Zvars", "runSuperLearner", "AIRHome", "tv_dir_val", "tv_threshold_val", "ov_dir_val", "ov_threshold_val", "df_vars", "processResults", "model_yn", "log_file")) %dopar% {
        i <- combos[k, "i"]
        j <- combos[k, "j"]
        settings <- data.frame(doc_title = paste0(i,"-",j),
                                  nfold = 20,
                                  Z_level = j,
                                  varName = i,
                                  confounders = paste0(Zvars[Zvars$name == i & Zvars$grp == j,]$Z, collapse = " "))
        # write.csv(settings, file = "settings_log.csv", append = TRUE)
        tryCatch({
          runSuperLearner(settings, AIRHome, tv_dir_val, tv_threshold_val, ov_dir_val, ov_threshold_val, log_file)
        # runSuperLearner(settings, AIRHome, tv_dir, tv_threshold, ov_dir, ov_threshold)
        }, error = function(e) {
          errMsg <- sprintf("SuperLearner: Error in combination i=%s, j=%s: %s", i, j, conditionMessage(e))
          cat(errMsg, file = log_file, sep = "\n", append = TRUE)
          NULL
        })
      }
    # }
    # Don't fotget to stop the cluster
    stopCluster(cl = cluster)
    incProgress(0.2, message = "Processing Results")
    cat("Successfully closed parallel cluster\n", file = log_file, append = TRUE)


    for (i in unique(Zvars$name)) {
      for (j in unique(Zvars$grp)) {
        settings <- data.frame(doc_title = paste0(i,"-",j),
                               nfold = 20,
                               Z_level = j,
                               varName = i,
                               confounders = paste0(Zvars[Zvars$name == i & Zvars$grp == j,]$Z, collapse = " "))
        tryCatch({
          if (i == tail(unique(Zvars$name), 1) & j == tail(unique(Zvars$name), 1) ) {
            move_results <- TRUE
          } else { move_results <- FALSE }
          processResults(settings, AIRHome, tv_dir_val, tv_threshold_val, ov_dir_val, ov_threshold_val, model_in(), model_yn, model_ate, log_file, move_results)
          }, error = function(e) {
            errMsg <- sprintf("Results Processing: Error in combination i=%s, j=%s: %s", i, j, conditionMessage(e))
            cat(errMsg, file = log_file, sep = "\n", append = TRUE)
            NULL
          })
        }
      }
    
    
    calc_complete(TRUE)
    sendSweetAlert(
      session = shiny::getDefaultReactiveDomain(),
      title = "Causal Estimates Successfully Calculated",
      text = "Please switch to the 'Results' tab to view your results.",
      type = "success",
      btn_labels = "Continue",
      btn_colors = "#3085d6",
      closeOnClickOutside = TRUE,
      showCloseButton = FALSE,
      )
  })
})




### output definitions ------------------------------------------------------------------

output$ui_graph_pane = renderUI({
  grVizOutput('blankGraph')
})


output$second_column_content <- renderUI({
    if (calc_complete()) {
      tags$div(
        style = "display: flex; flex-direction: column; height: 100%;",
        tags$div(
          style = "flex: 0 0 25%;",
          uiOutput("ui_ribbon_plot")
        ),
        tags$div(
          style = "flex: 0 0 25%;",
          uiOutput("ui_figurecaption")
        ),
        tags$hr(
          style = "border: none; border-top: 1px solid #ccc; margin: 5px 0;"
        ),
        tags$div(
          style = "flex: 1;",
          uiOutput("ui_interpretation")
        )
      )
    } else {
      tags$div(
        tags$div(
          style = "flex: 0 0 25%",
          plotOutput('histogram_x')
        ),
        tags$div(
          style = "flex: 0 0 25%",
          plotOutput('histogram_y')
        )
      )
    }
  })

output$ui_dl_btn <- renderUI({
  req(calc_complete())
  downloadBttn(
              outputId = "download_report",
              style = "jelly",
              color = "primary"
            )
})



output$step3 = renderUI({
  req(graph_complete())
  tagList(
    hr(),
    h4("Step 2: Select your variables of interest:")
  )
})

output$xvar = renderUI({
  req(graph_complete())  
  selectInput('xvar', 'Experimental (X) variable:', c("", names(df())),
              selected = ""
              )

  # xvar = "scenario_main_base"
  # xvar = "humidity"
})

output$yvar = renderUI({
  req(input$xvar)  
  x_desc <- get_X_descendents(input$xvar, AIRHome)
  choices <- setdiff(x_desc, input$xvar)
  selectInput('yvar', 'Outcome (Y) variable:', c("",choices), 
              selected = ""
              )
  # yvar = "images_acquired"
})


output$ui_threshold_x = renderUI({
  req(input$xvar)
  slider_range <- c(min(df()[[input$xvar]]), max(df()[[input$xvar]]))
  slider_step <- (slider_range[2] - slider_range[1]) / 10
   # Use Flexbox for inline alignment
    tags$div(
      style = "display: flex; align-items: center; flex-wrap: wrap;",
      
      # Part 1: Variable Selection
      tags$span(""),
      tags$span("is considered treated when it is "),
      
      # Part 2: Operator Selection
      tags$div(
        style = "margin-right: 5px;",
        selectInput("tv_dir", NULL, 
                    choices = c(">", ">=", "<", "<=", "="), 
                    width = "60px")
        ),
      # Part 3: Threshold Input
      tags$div(
        style = "margin-right: 5px;",
        numericInput("tv_threshold", NULL, 
                     value = mean(slider_range), 
                     step = slider_step,
                     width = "80px")
        )
    )
  
    # tv_dir = "<="
    # tv_threshold = 0
})

output$ui_threshold_y = renderUI({
  req(input$yvar)
  slider_range <- c(min(df()[[input$yvar]]), max(df()[[input$yvar]]))
  slider_step <- (slider_range[2] - slider_range[1]) / 10
   # Use Flexbox for inline alignment
    tags$div(
      style = "display: flex; align-items: center; flex-wrap: wrap;",
      
      # Part 1: Variable Selection
      tags$span(""),
      tags$span("is considered a success when it is "),
      
      # Part 2: Operator Selection
      tags$div(
        style = "margin-right: 5px;",
        selectInput("ov_dir", NULL, 
                    choices = c(">", ">=", "<", "<=", "="), 
                    width = "60px")
        ),
      # Part 3: Threshold Input
      tags$div(
        style = "margin-right: 5px;",
        numericInput("ov_threshold", NULL, 
                     value = mean(slider_range), 
                     step = slider_step,
                     width = "80px")
        )
    )
  
    # ov_dir = "<="
    # ov_threshold = 0
})

output$step2 = renderUI({
  req(input$file1)
  h4("Upload knowledge file:")
})

output$ui_file2 = renderUI({
  req(input$file1)
  fileInput("file2", "", accept = ".csv")
})

output$blankGraph <- renderGrViz({
  req(graph_complete())
  
  dot <- get_updated_graph(AIRHome, graph_update(), input$xvar, input$yvar, Zvars)
  grViz(dot)
})

output$histogram_x <- renderPlot({
  req(input$xvar, input$tv_dir, input$tv_threshold)
    
  p <- get_histogram_x(df(), input$xvar, input$tv_dir, input$tv_threshold)
  p
  }, bg = "transparent")

output$histogram_y <- renderPlot({
    req(input$yvar, input$ov_dir, input$ov_threshold)
  p <- get_histogram_y(df(), input$yvar, input$ov_dir, input$ov_threshold)
  p
  }, bg = "transparent")

output$ui_model_exist = renderUI({
  req(graph_update())
  radioGroupButtons(
    inputId = "model_exist",
    label = "Do you have an existing model?",
    choiceNames = c("Yes: I can upload it", "Yes: I can provide an ATE", "No: Do it all for me"),
    choiceValues = c("Yes", "ATE", "No"), 
    selected = "ATE",
    individual = TRUE,
    checkIcon = list(
      yes = tags$i(class = "fa fa-circle", 
                   style = "color: steelblue"),
      no = tags$i(class = "fa fa-circle-o", 
                  style = "color: steelblue"))
  )
})

output$ui_ate_upload = renderUI({
  req(graph_update())
  req(input$model_exist)
  if (input$model_exist == "ATE") {
    numericInput("ate_in", label = "ATE: ", value = 0, min = -1, max = 1, step = 0.1)
    # model_exist <- "ATE"
    # ate_in <- 0
  } else (return(NULL))
  
})

output$ui_model_upload = renderUI({
  req(input$model_exist)
  if (input$model_exist == "Yes") {
    fileInput("model_in", "", 
              accept = c(".rds", ".rda", ".model"))
  } else (return(NULL))
})

output$step4 = renderUI({
  req(graph_update())
  tagList(
    hr(),
    h4("Step 3: Tell us about your model:")
  )
})


output$ui_graphViz = renderUI({
  req(calc_complete())  
  h4("Causal graph")
  grVizOutput("graphViz")
})

output$ui_ci_plot = renderUI({
  req(calc_complete())  
  h4("Comparison of ATE for AIR and ML")
  plotOutput("ci_plot")
})

output$ui_ribbon_plot = renderUI({
  req(calc_complete())  
  h4("Comparison of ATE for AIR and ML")
  imageOutput("ribbon_plot")
})

output$ui_figurecaption = renderUI({
  req(calc_complete())
  uiOutput("figurecaption")
})

output$ui_goButton = renderUI({
  req(graph_update())
  actionBttn(
    inputId = "goButton",
    label = "Calculate Results",
    style = "jelly", 
    color = "primary"
  )
})

output$ui_buildButton = renderUI({
  req(file_check())
  actionBttn(
    inputId = "buildButton",
    label = "Build Graph",
    style = "jelly", 
    color = "primary"
    )
})

output$ui_updateButton = renderUI({
  req(input$yvar)
  actionBttn(
    inputId = "updateButton",
    label = "Update Graph",
    style = "jelly",
    color = "primary"
    )
})

output$graphViz = renderGrViz({
  req(calc_complete())
  
  dot <- get_final_graph(AIRHome, input$xvar, input$yvar, Zvars)
  grViz(dot)
})
  

# output$ribbon_plot = renderImage({
output$ribbon_plot = renderPlot({
  req(calc_complete())  
  p <- get_ribbon_plot(AIRHome)
  p  
}, bg = "transparent")

output$figurecaption = renderUI({
  req(calc_complete())
  caption <- get_figure_caption(AIRHome, df_vars)
  tags$div(style = "font-size:12px;", caption)
  })

output$ui_interpretation = renderUI({
  req(calc_complete())  

  result_text <- get_ui_interpretation(AIRHome, df_vars, Zvars)

  tagList(
    tags$h3("Interpreting your results:"),
    tags$div(style = "font-size:24px;", result_text)
  )
})


output$download_report <- downloadHandler(
  filename = function() {
    paste0('AIRTool-Report_', Sys.Date(), '.pdf')
    },
    content = function(file) {
      # Pre-evaluate reactive values
      loc_xvar <- input$xvar
      loc_yvar <- input$yvar
      loc_df <- df()
      loc_tv_dir <- input$tv_dir
      loc_tv_threshold <- input$tv_threshold
      loc_ov_dir <- input$ov_dir
      loc_ov_threshold <- input$ov_threshold
      loc_df_vars <- df_vars
      loc_Zvars <- Zvars
      loc_graph_update <- graph_update()
      loc_figure_cap <- get_figure_caption(AIRHome, df_vars)
      loc_result_text <- get_ui_interpretation(AIRHome, df_vars, Zvars)
    
      # Save plots
      save_ggplot_to_png(get_histogram_x(loc_df, loc_xvar, loc_tv_dir, loc_tv_threshold), "plots/xhist.png")
      save_ggplot_to_png(get_histogram_y(loc_df, loc_yvar, loc_ov_dir, loc_ov_threshold), "plots/yhist.png")
      save_ggplot_to_png(get_ribbon_plot(AIRHome), "plots/ribbon.png")
      save_graphviz_to_png(get_updated_graph(AIRHome, loc_graph_update, loc_xvar, loc_yvar, loc_Zvars), "plots/updatedgraph.png")
      save_graphviz_to_png(get_final_graph(AIRHome, loc_xvar, loc_yvar, loc_Zvars), "plots/finalgraph.png")
    
      # Render Quarto report
      quarto::quarto_render(
        input = "scripts/AIRReport.qmd",
        output_format = "pdf",
        execute_params = list(
          AIRHome = AIRHome,
          xvar = loc_xvar,
          yvar = loc_yvar,
          figure_cap = loc_figure_cap,
          result_text = loc_result_text
        )
      )
    
      # Manually find the generated file
      generated_file_path <- "scripts/AIRReport.pdf"
    
      # Make sure it actually exists before copying
      if (!file.exists(generated_file_path)) {
        stop("Failed to find generated PDF at ", generated_file_path)
      }
    
      # Now copy it to where Shiny expects it
      file.copy(generated_file_path, file, overwrite = TRUE)
    }
)
```

# Key

-   Graph Colors
    -   [Yellow]{style="color: #FFC107; font-weight: bold;"}: Variable of interest, selected by the user in step 2. Both X and Y variables are shaded yellow to quickly draw the attention of the user to their selected variables.
    -   [Dark Gray]{style="color: #9394A2; font-weight: bold;"}: Any nodes with this color have been identified as belonging to the first identified adjustment set, used to calculate causal effect estimates.
    -   [Light Gray]{style="color: #D4C7C7; font-weight: bold;"}: Any nodes with this color have been identified as belonging to the second identified adjustment set, used to calculate causal effect estimates.
    -   [Red]{style="color: #C00000; font-weight: bold;"}: Any nodes with this color have been flagged as introducing bias into the results of the input classifier. Nodes will change from (dark/light) gray to red if the classifier ATE falls outside the 95% confidence interval for a given adjustment set.
-   Histogram Colors
    -   [Blue]{style="color: #5D9AFF; font-weight: bold;"}: This is the 'treated' or 'success' portion of the data. Data falling within this range are categorized as 1. This represents the presence of a treatment, success, category of interest, etc...
    -   [Gray]{style="color: #EAE1D7; font-weight: bold;"}: This is the 'untreated' or 'fail' portion of the data. Data falling within this range are categorized as 0. This represents the absence of a treatment, success, category of interest, etc...
-   Ribbon Plot Colors
    -   [Red]{style="color: #C00000; font-weight: bold;"}: The range of effect sizes that are outside the 95% confidence intervals of both adjustment sets. Values falling in this range are considered non-significant.
    -   [Yellow]{style="color: #FCB514; font-weight: bold;"}: The range of effect sizes that are outside of one 95% confidence interval for one effect size, but inside for the other. Values falling in this range are considered suspect, and should be closely monitored for signs of bias.
    -   [Green]{style="color: #378855; font-weight: bold;"}: The range of effect sizes that are inside both adjustment set's 95% confidence intervals. Values falling in this range are consistent with those calculated by AIR's causal estimation and are considered bias-free.
